---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggdescdist

<!-- badges: start -->
<!-- badges: end -->

This is a simple package with a simple goal: Produce a Cullen and Frey skewness-kurtosis plot using `ggplot2`. The underlying code is adapted from the `fitdistrplus` package, where the `descdist` function provides a skewness-kurtosis plot using base R graphics. The `ggplot2` version attempts to recreate the look and function of that plot, but with more elegant theme elements. The beauty of `ggplot2` is that the resulting plot is fully customizable. If desired, all theme elements can be turned off, producing a plot using the default `ggplot2` theme.

## Installation

You can install the development version of `ggdescdist` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mwaak/ggdescdist")
```

## Example

Note that `fitdistrplus` is not a dependency for this package. If you wish to compare this plot to the original, then `fitdistrplus` must be installed separately.

First, create a simple normal distribution.
```{r setup}
library(ggdescdist)

set.seed(42)
x <- rnorm(1000, mean = 27, sd = 3)
```

Default skewness-kurtosis plot without bootstrapping:
```{r example_no_boot}
ggdescdist(x)
```

Skewness-kurtosis plot with bootstrapping:
```{r}
ggdescdist(x, boot = 20)
```

Compare to the original skewness-kurtosis plot ("fitdistrplus" must be installed):
```{r comparison}
if ("fitdistrplus" %in% installed.packages()){
  fitdistrplus::descdist(x)
}
```
